%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Justin}{Childress}
\position{Design Engineer}
\address{Knoxville, Tennessee}

\mobile{(423) 991-8996}
\email{jchildress704@gmail.com}
\github{JChildress704}
\linkedin{www.linkedin.com/in/Justin-W-Childress}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[L]

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{Cover Letter}
Hello,

I am interested in an engineering position at ORNL and believe I am well equipped for it. For the past six years I have been working as or adjacent to data engineers. During that time I completed my Master's in Aerospace Engineering and am now excited to apply that degree to my career. I have lived in Knoxville for about 10 years now, and my friends who have worked in or around ORNL have always sounded interested in and happy about their jobs there which makes it sound like a team I'd love to be a part of!

My career so far has given me a strong background in coding, specifically python and SQL and those skills are applicable to many programming languages. During my time in Graduate School my focus was on computational fluid dynamics, finite element analysis, and data science. Since it was aerospace engineering, this included an understanding of turbomachinery and high energy fluid dynamics.

The commonality with my time as a student and as a data engineer has been examining a technical problem, breaking it down into the component steps, and proceeding to solve those. I believe that this skillset would be useful in a broad range of engineering positions and would be thrilled to apply it at ORNL.

Thank you for your time, I hope to hear from you soon!

\end{cvletter}

\end{document}